tl22-01_analysingAssemblyStats

### 2022-10-21 chapter5_results_vivaxDeNovo/tl22-01_VvxBUSCO.Rmd
Add many required vivax files and change paths in vivax scripts

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('readr')
library('dplyr', 
        lib.loc = "/camp/home/littlet/R/x86_64-pc-linux-gnu-library/4.0")
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('seqinr')
library(plotly)
```

```{r analyse_busco}
samplesheet <- read.delim("/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/samplesheet.txt")

samplesheet_busco.df <- lapply(unique(samplesheet$assembly), 
                               function(assembly.file){
                                 # The tenth element in the file path string corresponds to the assembly names that I used.
                                 assembly <- strsplit(assembly.file, split = '/')[[1]][10]
                                 if(!is.na(assembly)){
                                   busco.file <- paste0('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/busco/',
                                                        assembly)
                                   #Skip 2 in the read_tsv function as the first two lines are not part of the data frame.
                                   busco_api.df <- read_tsv(paste0(busco.file, 
                                                                   '_apicomplex/run_apicomplexa_odb10/full_table.tsv'),
                                                            skip = 2,
                                                            show_col_types = FALSE)
                                   busco_api.complete <- sum(busco_api.df$Status == "Complete")
                                   busco_api.fragment <- sum(busco_api.df$Status == "Fragmented")
                                   busco_api.duplicate <- sum(n_distinct(
                                     busco_api.df$`# Busco id`[busco_api.df$Status == "Duplicated"]
                                   ))

                                   busco_plasmo.df <- read_tsv(paste0(busco.file, 
                                                                      '_plasmodium/run_plasmodium_odb10/full_table.tsv'),
                                                               skip = 2,
                                                               show_col_types = FALSE)
                                   busco_plasmo.complete <- sum(busco_plasmo.df$Status == "Complete")
                                   busco_plasmo.fragment <- sum(busco_plasmo.df$Status == "Fragmented")
                                   busco_plasmo.duplicate <- sum(n_distinct(
                                     busco_plasmo.df$`# Busco id`[busco_plasmo.df$Status == "Duplicated"]
                                   ))

                                   data.frame(
                                     assembly = assembly.file,
                                     assembly_name = assembly,
                                     Experiment = samplesheet$Experiment[match(assembly.file, samplesheet$assembly)],
                                     num_busco_api_complete = busco_api.complete,
                                     perc_busco_api_complete = round(100*busco_api.complete/446,
                                                                     digits = 3),
                                     num_busco_api_fragment = busco_api.fragment,
                                     perc_busco_api_fragment = round(100*busco_api.fragment/446,
                                                                     digits = 3),
                                     num_busco_api_duplicate = busco_api.duplicate,
                                     perc_busco_api_duplicate = round(100*busco_api.duplicate/446,
                                                                      digits = 3),
                                     perc_busco_api_nonMissing = round(100*(
                                       busco_api.fragment+busco_api.complete+busco_api.duplicate)/446,
                                       digits = 3
                                     ),

                                     num_busco_plasmo_complete = busco_plasmo.complete,
                                     perc_busco_plasmo_complete = round(100*busco_plasmo.complete/3642,
                                                                        digits = 3),
                                     num_busco_plasmo_fragment = busco_plasmo.fragment,
                                     perc_busco_plasmo_fragment = round(100*busco_plasmo.fragment/3642,
                                                                        digits = 3),
                                     num_busco_plasmo_duplicate = busco_plasmo.duplicate,
                                     perc_busco_plasmo_duplicate = round(100*busco_plasmo.duplicate/3642,
                                                                         digits = 3),
                                     perc_busco_plasmo_nonMissing = round(100*(
                                       busco_plasmo.fragment+busco_plasmo.complete+busco_plasmo.duplicate)/3642,
                                       digits = 3
                                     )
                                   )
                                 } else { return(NULL) }
                               }) %>% bind_rows
```

```{r plotly}

#Get the number of pirs stats
assembly_stats.df <- read.table('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/tl22-01_assembly_info_extra.txt')

@@

assembly_stats_busco <- inner_join(assembly_stats.df, 
                                   mutate(samplesheet_busco.df, 
                                          assembly_file = assembly), 
                                   by = 'assembly_file')
# write.table(assembly_stats_busco,
#             '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/tl22-01_assembly_info_extra_busco.txt')

#Include '.+(?=0.95)' pattern for searching as Gunalan has multiple cdhitest threshold assemblies.
samplesheet_busco.df <- mutate(rowwise(samplesheet_busco.df), 
                               num_pir_predict = assembly_stats.df$num_uniq_mRNA_ORFs_over200aaLength[
                                 str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                         '.+(?=0.95)'))
                               ],
                               expt_num = unique(
                                 assembly_stats.df$experiment_num[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ]),
                               num_transcripts = unique(
                                 assembly_stats.df$num_transcripts[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ]),
                               num_mRNA_pir_over200aa_over1TPM = unique(
                                 assembly_stats.df$num_mRNA_pir_over200aa_over1TPM[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ])
)

hline <- function(y = 0, color = "blue") {
  list(
    type = "line", 
    x0 = 0, 
    x1 = 1, 
    xref = "paper",
    y0 = y, 
    y1 = y, 
    line = list(color = 'black')
  )
}
vline <- function(x = 0, color = "red") {
  list(
    type = "line", 
    y0 = 0, 
    y1 = 1, 
    yref = "paper",
    x0 = x, 
    x1 = x, 
    line = list(color = color)
  )
}

@@

ggsave(plot = plot_buscos,
       '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/plots/assemblies_buscoPlasmo-buscoApi-pirNum.pdf',
       device = 'pdf',
       width = 7,
       height = 7,
       units = "in")

>>>>

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('readr')
library('dplyr')
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('seqinr')
library(plotly)
```

```{r read_busco}
samplesheet <- read.delim("samplesheet.txt")

#Get the number of pirs stats
assembly_stats.df <- read.table('tl22-01_assembly_info_extra.txt')

@@

assembly_stats_busco <- read.table('tl22-01_assembly_info_extra_busco.txt')

#Include '.+(?=0.95)' pattern for searching as Gunalan has multiple cdhitest threshold assemblies.
samplesheet_busco.df <- mutate(rowwise(assembly_stats_busco), 
                               num_pir_predict = assembly_stats.df$num_uniq_mRNA_ORFs_over200aaLength[
                                 str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                         '.+(?=0.95)'))
                               ],
                               expt_num = unique(
                                 assembly_stats.df$experiment_num[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ]),
                               num_transcripts = unique(
                                 assembly_stats.df$num_transcripts[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ]),
                               num_mRNA_pir_over200aa_over1TPM = unique(
                                 assembly_stats.df$num_mRNA_pir_over200aa_over1TPM[
                                   str_detect(assembly_stats.df$assembly, pattern = paste0(assembly_name, 
                                                                                           '.+(?=0.95)'))
                                 ])
)
```

```{r plotly}
hline <- function(y = 0, color = "blue") {
  list(
    type = "line", 
    x0 = 0, 
    x1 = 1, 
    xref = "paper",
    y0 = y, 
    y1 = y, 
    line = list(color = 'black')
  )
}
vline <- function(x = 0, color = "red") {
  list(
    type = "line", 
    y0 = 0, 
    y1 = 1, 
    yref = "paper",
    x0 = x, 
    x1 = x, 
    line = list(color = color)
  )
}

@@

ggsave(plot = plot_buscos,
       'plots/assemblies_buscoPlasmo-buscoApi-pirNum.pdf',
       device = 'pdf',
       width = 7,
       height = 7,
       units = "in")

### 2022-10-21 chapter5_results_vivaxDeNovo/tl22-01_VvxSalmonAlignment.Rmd
Add many required vivax files and change paths in vivax scripts

This script analyses the results of a _de novo_ assembly of Plasmodium vivax RNAseq data.

@@

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('readr')
library('dplyr', 
        lib.loc = "/camp/home/littlet/R/x86_64-pc-linux-gnu-library/4.0")
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('seqinr')
```

@@

```{r load_data}
pir.info <- read.csv('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/github_project/tl22-01_vivaxDeNovo/PlasmoDBv56_VvxPirs_P01_Sal1.csv', 
                     header = TRUE)
```

```{r de_novo_pir_list}
# pir_lists.dir <- "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/hmmer/scspades/"
# pir_lists.files <- list.files(pir_lists.dir, 
#                               pattern = '0.95cdhitest_hmmerPfam-PlasmodiumVir.list',
#                               full.names = TRUE) %>% 
#   #Get those with file sizes above zero (no empty lists)
#   # file.info gets the file sizes
#   .[file.info(., extra_cols = FALSE)$size > 0]
# 
# # Read the pirs into a list (as a vector).
# # sapply through the file list, read in the table and subset with the automatic column name V1
# pir_list.vec <- unlist(
#   sapply(pir_lists.files, 
#          function(pir_list){
#            #str_removing the _1 at the end of the removal 
#            str_remove(read.table(pir_list)$V1, 
#                       pattern =  '_[[:digit:]]$')
#          })
# )

#Need to read in the >200aa ORF length  pirs
pir_list.vec <- str_extract(names(read.fasta('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/hmmer/scspades/G18_B20_C19_Z16_M19_R20_K1719_G19-cat/G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta')),
                                  pattern = 'NODE.+(?=_[[:digit:]])')

@@

```{r load_cluster_data}
node.df <- read.csv('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/networks/tpmOver1/sequence-MCLclusters_tpmOver1_30pid25lngthI14.csv') %>% 
  #Convert the cluster numbers to a factor as they are discrete categories.
  mutate(across(contains('lngth'), factor))
```

```{r define_subfam}
cluster_subfam.df <- read.csv('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/networks/tpmOver1/cluster_subfam_30pid25lngthI1.4.csv')

@@

```{r load_salmon}
#Get the full file paths of the salmon quant.sf files.
quant_files <- list.files(path = "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/salmon/all_files",
                          recursive = TRUE,
                          pattern = 'quant.sf',
                          full.names = TRUE)

#Load the samplesheet.txt file of metadata, add new column for salmon files
samplesheet <- read.delim("/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/samplesheet.txt") %>% 
  mutate(salmon_quant = '')

@@

'noCluster' means that the pir sequence was not in the '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/gephi/G18_B20_C19_Z16_M19_R20_K1719_G19-cat/nodes_mcl_50pid100lngthNoSame2Same.csv' file.
I think this means that they didn't have any BLAST similarity to other pir to the thresholds:
* 50% id.
* alignment >=100aa.

```{r save_quant}
lapply(names(expt_quant), 
       function(expt){
         lapply(names(expt_quant[[expt]]), 
                function(assembly){
                  if(!is.null(expt_quant[[expt]][[assembly]])){
                    #Make the directories to save the files in. Recursive = TRUE so that it will make parents t
                    # dir.create(paste( "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/quantFiles_R",
                    #                   expt, assembly, sep = '/'),
                    #            recursive = TRUE)
                    write.csv(expt_quant[[expt]][[assembly]],
                              file = paste( "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/quantFiles_R",
                                            expt, assembly,
                                            paste0('quant_', 
                                                   assembly,
                                                   '_subfam30pid25lngthI14.csv'),
                                            sep = '/'),
                              row.names = FALSE
                    )
                  }
                })
       })
```

>>>>

This script reads the Salmon files and assigns them cluster numbers from the networks.

@@

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('readr')
library('dplyr')
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('seqinr')
```

@@

```{r load_data}
pir.info <- read.csv('PlasmoDBv56_VvxPirs_P01_Sal1.csv', 
                     header = TRUE)
```

```{r de_novo_pir_list}
#Need to read in the >200aa ORF length  pirs
pir_list.vec <- str_extract(names(read.fasta('G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta')),
                                  pattern = 'NODE.+(?=_[[:digit:]])')

@@

```{r load_cluster_data}
node.df <- read.csv('sequence-MCLclusters_tpmOver1_30pid25lngthI14.csv') %>% 
  #Convert the cluster numbers to a factor as they are discrete categories.
  mutate(across(contains('lngth'), factor))
```

```{r define_subfam}
cluster_subfam.df <- read.csv('cluster_subfam_30pid25lngthI1.4.csv')

@@

```{r load_salmon}
#Get the full file paths of the salmon quant.sf files.
quant_files <- list.files(path = "salmon/all_files",
                          recursive = TRUE,
                          pattern = 'quant.sf',
                          full.names = TRUE)

#Load the samplesheet.txt file of metadata, add new column for salmon files
samplesheet <- read.delim("samplesheet.txt") %>% 
  mutate(salmon_quant = '')

@@

'noCluster' means that the pir sequence was not in the 
'nodes_mcl_50pid100lngthNoSame2Same.csv' file.
I think this means that they didn't have any BLAST similarity to other pir to the thresholds:
* 50% id.
* alignment >=100aa.

```{r save_quant}
lapply(names(expt_quant), 
       function(expt){
         lapply(names(expt_quant[[expt]]), 
                function(assembly){
                  if(!is.null(expt_quant[[expt]][[assembly]])){
                    #Make the directories to save the files in. Recursive = TRUE so that it will make parents t
                    # dir.create(paste( "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/quantFiles_R",
                    #                   expt, assembly, sep = '/'),
                    #            recursive = TRUE)
                    write.csv(expt_quant[[expt]][[assembly]],
                              file = paste( "quantFiles_R",
                                            expt, assembly,
                                            paste0('quant_', 
                                                   assembly,
                                                   '_subfam30pid25lngthI14.csv'),
                                            sep = '/'),
                              row.names = FALSE
                    )
                  }
                })
       })
```

### 2022-10-21 chapter5_results_vivaxDeNovo/tl22-01_VvxSalmonAnalysis.Rmd
Add many required vivax files and change paths in vivax scripts

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('dplyr', 
        # lib.loc = "/camp/home/littlet/R/x86_64-pc-linux-gnu-library/4.0"
        )
library('readr')
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('data.table')
library('ggpubr')
library('seqinr')
```

@@

samplesheet <- read.delim("/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/samplesheet.txt")

@@

expt_num.df <- read.csv('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/github_project/tl22-01_vivaxDeNovo/expt_codes.csv')

expt_quant <- lapply(unique(samplesheet$Experiment),
                     function(expt){
                       #Get the experiment code.
                       expt_code <- expt_num.df$expt_code[match(expt, 
                                                                expt_num.df$expt)]
                         assembly.list <- lapply(unique(samplesheet$assembly[samplesheet$Experiment == expt]),
                                                 function(assembly_file){
                                                   assembly <- str_extract(assembly_file,
                                                                           pattern = '(?<=cdhitest\\/).+(?=\\/)')
                                                   #Get the file name by pasting the words together
                                                   quant_file <- paste(
                                                     "/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/quantFiles_R",
                                                     expt, assembly, 
                                                     paste0('quant_', 
                                                            assembly,
                                                            '_subfam30pid25lngthI14.csv'
                                                     ),
                                                     sep = '/')
                                                   if(file_test("-f", quant_file)){
                                                     #If the file exists then we can read it in
                                                     quant_csv <- read.csv(quant_file, 
                                                                           header = TRUE)
                                                     return(quant_csv)
                                                   }
                                                 })
                         #Get the names for the list of assemblies, extract the important bits and replace the expt with the expt_code.
                         names(assembly.list) <- str_replace(
                           str_extract(unique(samplesheet$assembly[samplesheet$Experiment == expt]),
                                       pattern = '(?<=cdhitest\\/).+(?=\\/)'), 
                           pattern = expt,
                           replacement = expt_code)
                         return(assembly.list)
                     })

@@

```{r pir_diversity_v_BUSCOs}
buscos <- read.table('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/tl22-01_assembly_info_extra_busco.txt')

@@

                   if(global_save_var){
                     ggsave(
                       plot = cowplot::plot_grid(apl, bpl, ncol = 2),
                       filename = paste0(
                         '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/plots/salmonQuant_plots/tl22-01_',
                         expt, '_', absolute_or_norm, '_', assembly,
                         '_quantSalmon_stacked_subfam30pid25lngthI14.pdf'
                       ),
                       width = 7,
                       height = 5,
                       units = "in",
                       dpi = 330
                     )
                   }

@@

if(global_save_var){
  ggsave(
    plot = legend.plot,
    filename = '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/plots/salmonQuant_plots/tl22-01_legend_quantSalmon_stacked_subfam30pid25lngthI14.pdf',
    width = 7,
    height = 5,
    units = "in",
    dpi = 330
  )
}
```

@@

G18G19_hmmerVir200aa.fa <- read.fasta('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/hmmer/scspades/G18_B20_C19_Z16_M19_R20_K1719_G19-cat/G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta')

@@

# write.fasta(G18G19_hmmerVir200aa_tpmOver1.fa,
#             names(G18G19_hmmerVir200aa_tpmOver1.fa),
#             file.out = '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/hmmer/scspades/G18_B20_C19_Z16_M19_R20_K1719_G19-cat/G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_orf200aa_tpmOver1.fasta')

@@

```{r Num-pir-transcript_v_Num-transcript-total}
assembly_info.df <- read.delim('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/tl22-01_assembly_info.txt') %>% 
  filter(!grepl(assembly, pattern = '0\\.9c|0\\.99'),
         !grepl(assembly, pattern = 'SRX5158513_SRR8347514|SRX5158512_SRR8347515'))  
#Filter out any none-0.95 assembly made. And potential Kim19_A duplicate?

@@

expt_num.df <- data.frame(expt = expt_num.vec, 
                          expt_code = names(expt_num.vec), 
                          col = c(colours_val,colours_val['E07'],colours_val['E08']))
# write.csv(expt_num.df,
#           file = '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/github_project/tl22-01_vivaxDeNovo/expt_codes.csv',
#           row.names = FALSE)

@@

if(global_save_var){
  ggsave(plot = plot,
         '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/plots/assemblies_numPirTranscripts_totalTranscripts.pdf',
         device = 'pdf',
         width = 7,
         height = 5,
         units = "in")
}
```

ISSUE: Why is the number of sequences in '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/hmmer/scspades/G18_B20_C19_Z16_M19_R20_K1719_G19-cat/G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta' larger than sum(assembly_info_samplesheet.df£$num_uniq_mRNA_pirHMMerORFs_nomatch95known_over200aa)

>>>>

```{r loading_packages, include = FALSE, message = FALSE}
# Load the required packages
library('dplyr')
library('readr')
library('stringr')
library('purrr')
library('kableExtra')
library('plotly')
library('rmarkdown')
library('data.table')
library('ggpubr')
library('seqinr')
```

@@

samplesheet <- read.delim("samplesheet.txt")

@@

expt_num.df <- read.csv('expt_codes.csv')

expt_quant <- lapply(unique(samplesheet$Experiment),
                     function(expt){
                       #Get the experiment code.
                       expt_code <- expt_num.df$expt_code[match(expt, 
                                                                expt_num.df$expt)]
                         assembly.list <- lapply(unique(samplesheet$assembly[samplesheet$Experiment == expt]),
                                                 function(assembly_file){
                                                   assembly <- str_extract(assembly_file,
                                                                           pattern = '(?<=cdhitest\\/).+(?=\\/)')
                                                   #Get the file name by pasting the words together
                                                   quant_file <- paste(
                                                     "quantFiles_R",
                                                     expt, assembly, 
                                                     paste0('quant_', 
                                                            assembly,
                                                            '_subfam30pid25lngthI14.csv'
                                                     ),
                                                     sep = '/')
                                                   if(file_test("-f", quant_file)){
                                                     #If the file exists then we can read it in
                                                     quant_csv <- read.csv(quant_file, 
                                                                           header = TRUE)
                                                     return(quant_csv)
                                                   }
                                                 })
                         #Get the names for the list of assemblies, extract the important bits and replace the expt with the expt_code.
                         names(assembly.list) <- str_replace(
                           str_extract(unique(samplesheet$assembly[samplesheet$Experiment == expt]),
                                       pattern = '(?<=cdhitest\\/).+(?=\\/)'), 
                           pattern = expt,
                           replacement = expt_code)
                         return(assembly.list)
                     })

@@

```{r pir_diversity_v_BUSCOs}
buscos <- read.table('tl22-01_assembly_info_extra_busco.txt')

@@

                   if(global_save_var){
                     ggsave(
                       plot = cowplot::plot_grid(apl, bpl, ncol = 2),
                       filename = paste0(
                         'plots/salmonQuant_plots/tl22-01_',
                         expt, '_', absolute_or_norm, '_', assembly,
                         '_quantSalmon_stacked_subfam30pid25lngthI14.pdf'
                       ),
                       width = 7,
                       height = 5,
                       units = "in",
                       dpi = 330
                     )
                   }

@@

if(global_save_var){
  ggsave(
    plot = legend.plot,
    filename = 'plots/salmonQuant_plots/tl22-01_legend_quantSalmon_stacked_subfam30pid25lngthI14.pdf',
    width = 7,
    height = 5,
    units = "in",
    dpi = 330
  )
}
```

@@

G18G19_hmmerVir200aa.fa <- read.fasta('G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta')

@@

# write.fasta(G18G19_hmmerVir200aa_tpmOver1.fa,
#             names(G18G19_hmmerVir200aa_tpmOver1.fa),
#             file.out = 'G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_orf200aa_tpmOver1.fasta')

@@

```{r Num-pir-transcript_v_Num-transcript-total}
assembly_info.df <- read.delim('tl22-01_assembly_info.txt') %>% 
  filter(!grepl(assembly, pattern = '0\\.9c|0\\.99'),
         !grepl(assembly, pattern = 'SRX5158513_SRR8347514|SRX5158512_SRR8347515'))  
#Filter out any none-0.95 assembly made. And potential Kim19_A duplicate?

@@

expt_num.df <- data.frame(expt = expt_num.vec, 
                          expt_code = names(expt_num.vec), 
                          col = c(colours_val,colours_val['E07'],colours_val['E08']))
# write.csv(expt_num.df,
#           file = 'expt_codes.csv',
#           row.names = FALSE)

@@

if(global_save_var){
  ggsave(plot = plot,
         'plots/assemblies_numPirTranscripts_totalTranscripts.pdf',
         device = 'pdf',
         width = 7,
         height = 5,
         units = "in")
}
```

ISSUE: Why is the number of sequences in 'G18_B20_C19_Z16_M19_R20_K1719_G19-cat_scspades_0.95cdhitest_hmmerPfam-PlasmodiumVir_200aa.fasta' larger than sum(assembly_info_samplesheet.df£$num_uniq_mRNA_pirHMMerORFs_nomatch95known_over200aa)

### 2022-10-21 chapter5_results_vivaxDeNovo/tl22-01_analysingAssemblyStats.Rmd
Add many required vivax files and change paths in vivax scripts

```{r read_data}
df <- read.delim('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/tl22-01_assembly_info.txt')
```

@@

```{r expt_name}
 accession_table <- read.csv('/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/samples_to_cat.csv')

@@

```{r numNovPir_v_totalTranscripts}
(plot <- ggplot(data = df, aes(x = num_transcripts, 
                               y = num_uniq_mRNA_pirHMMerORFs_nomatch95known_over200aa,
                               col = experiment,
                               shape = tolower(Cat.Sample.stage.s.))) +
   geom_point() +
   scale_color_manual(values = safe_colorblind_palette) +
   scale_shape_manual(values=1:nlevels(df$Cat.Sample.stage.s.),
                      name = 'Life cycle stage') +
   xlab('Number of assembled transcripts') +
   ylab('Number of novel pir ORFs') +
   theme_classic() +
   theme(legend.text = element_text(size = 7),
         legend.title = element_text(size = 7),
         legend.box = 'horizontal'))
ggsave(plot = plot,
       '/camp/lab/langhornej/working/HPC/littlet/tl22-01_vivaxDeNovo/plots/assemblies_numNovPir_v_totalTranscripts.pdf',
       device = 'pdf',
       width = 7,
       height = 5,
       units = "in")
```

>>>>

```{r read_data}
df <- read.delim('tl22-01_assembly_info.txt')
```

@@

```{r expt_name}
 accession_table <- read.csv('samples_to_cat.csv')

@@

```{r numNovPir_v_totalTranscripts}
(plot <- ggplot(data = df, aes(x = num_transcripts, 
                               y = num_uniq_mRNA_pirHMMerORFs_nomatch95known_over200aa,
                               col = experiment,
                               shape = tolower(Cat.Sample.stage.s.))) +
   geom_point() +
   scale_color_manual(values = safe_colorblind_palette) +
   scale_shape_manual(values=1:nlevels(df$Cat.Sample.stage.s.),
                      name = 'Life cycle stage') +
   xlab('Number of assembled transcripts') +
   ylab('Number of novel pir ORFs') +
   theme_classic() +
   theme(legend.text = element_text(size = 7),
         legend.title = element_text(size = 7),
         legend.box = 'horizontal'))
ggsave(plot = plot,
       'plots/assemblies_numNovPir_v_totalTranscripts.pdf',
       device = 'pdf',
       width = 7,
       height = 5,
       units = "in")
```
